Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/results.tex
Fix mesh description

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
for the results presented in Figure 2a, in which they present reflectance measurements across wave number
for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
length of the pillars.

@@

\textit{mesh}
For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-uniform mesh of
approximately four thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

>>>>

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
for the results presented in Figure 2a, in which they present reflectance measurements across wave number
for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.

@@

\textit{mesh}

For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
the aspect ratio's variation study.
